Describing demographic models is hard

### 2020-05-20 paper.tex
title suggestions

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
}

>>>>

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
Lessons learned from misspecified models of human history \\
Lessons learned from buggy models of human history \\
Lessons learned from bugs in population genetics models
}
